%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Zachary}}}}} % First name
	% \colorbox{white}{{\HUGE\textcolor{black}{\textbf{\MakeUppercase{Fucken}}}}} % Middle name
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Lutz}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Senior Embedded Systems \\ Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Milwaukee, WI}\\
	\icon{Phone}{12}{+1 414 937 1801}\\
		
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	% \icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	\icon{At}{12}{\href{mailto:alyx@vance.me}{zacharyalutz@gmail.com}}\\
    \icon{Github}{12}{\href{https://github.com/alyxvance}{github.com/zacharyalutz}}\\
	% \icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@zachary_lutz}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
I am an experienced electrical engineer with a focus on firmware, embedded systems, and FPGA design. Over the past seven years, I've gained expertise in power conversion and communication protocols in the energy and aerospace sectors. A reliable team player and emerging leader, I combine my technical knowledge, adaptability, and leadership skills to drive the development of practical and sustainable engineering solutions.

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{C/C++}{95}
		\baritem{VHDL}{100}
		\baritem{Verilog}{60}
		\baritem{Tcl}{70}
		\baritem{Python}{65}
		\baritem{MATLAB}{75}
	\end{barchart}
\end{minipage}

%\begin{center}
	%\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2020 -- present}
		{Embedded Software + FPGA Developer}
		{Imagen Energy}
		{        \texttt{C/C++}\slashsep\texttt{VHDL}\slashsep\texttt{MATLAB}\slashsep\texttt{Simulink}\slashsep\texttt{Linux}\slashsep\texttt{Python}
        \begin{itemize}
            \item Software architecture, incl. communication interfaces, information security, data integrity.
            \item Team lead for software/firmware group.
            \item High-frequency real-time control design and implementation for power conversion in FPGA.
            \item EV charging standards and protocol implementation (CCS, CHAdeMO, ISO 15118, IEC 61851, DIN SPEC 70121)
            \item Embedded Linux distro customization, including device tree and BSP development using Yocto.
            \item Physical system modeling and simulation.
        \end{itemize}      
        }
	\entry
		{2017 -- 2020}
		{PLD Engineer II}
		{Astronautics Corporation}
		{        \texttt{VHDL}\slashsep\texttt{Verilog}\slashsep\texttt{Tcl}\slashsep\texttt{Simulink}\slashsep\texttt{Modelsim}
        \begin{itemize}
            \item Develop RTL for integrated avionics systems such as flight displays, flight surface control products, open architecture network server platforms, air-to-ground communication.
            \item Requirements capture and analysis for certified DAL A programs (as defined by DO-254).
            \item Clock domain partitioning, timing constraints rules, static timing closure.
            \item Lead verification engineer.
            \item Develop bus functional models for device simulation.
            \item Designed a PLD Department simulation environment framework, using concepts from OSVVM.
        \end{itemize}      
        }
	\entry
		{2015 -- 2017}
        {Engineering Intern}
		{Johnson Controls}
		{        \texttt{C}\slashsep\texttt{WiFi}\slashsep\texttt{ZigBee}\slashsep\texttt{Bluetooth}
        \begin{itemize}
            \item Advanced development team; evaluate and exploit emerging technologies for novel smart building applications.
            \item Power analysis of 2.4 GHz band radios
            \item Model Predictive Control (MPC) implementation in building automation controller networks.
        \end{itemize}      
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2013 -- 2016}
		{University of Wisconsin - Milwaukee}
		{B.S. Electrical Engineering}
		{Pt. Koshadhish Misra Memorial Award for electrical engineering excellence -- 3.95 GPA}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\cvsect{Skills/Tools}

\begin{minipage}[t]{0.30\textwidth} % 45% of the page width for name
\vspace{-\baselineskip} % Required for vertically aligning minipages
\textbf{SoC/FPGA Device Families:}\\
\textbf{Programming Languages:}\\
\textbf{Simulation/Synthesis:}\\
\textbf{Revision Control:}\\
\textbf{Requirements Management:}\\
\textbf{Agile/Scrum Management:}\\
\textbf{Communication Protocols:}\\
\textbf{Electronics Measurement:}\\
\textbf{Electronics Assembly:}\\
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.70\textwidth} % 45% of the page width for name
\vspace{-\baselineskip} % Required for vertically aligning minipages
Intel (Cyclone); Xilinx (Spartan, Zynq); Microsemi (IGLOO2)\\
C/C++, VHDL, Verilog, Tcl, Python, BitBake, Bash\\
MATLAB, ModelSim, Quartus, Xilinx ISE, Vivado, Libero\\
Git, Subversion (SVN)\\
DOORS\\
Team Foundation Server (TFS), Miro\\
Ethernet, SPI, CAN, UART, I2C, ARINC-429, PCIe, JTAG, WebSockets\\
Digital multimeter (DMM), oscilloscope, logic analyzer\\
Soldering iron, pick and place, reflow oven.\\
\end{minipage}


%----------------------------------------------------------------------------------------

\end{document}
